### 2020-02-12 article_draft.tex
Changes before moving sigma to estimator

\section{Proposed testing procedure}
\label{sec:prop_test_proc}
Let $\hat{\boldsymbol{\Psi}}(\boldsymbol{\rvo})$ be an estimator of $\boldsymbol{\psi}$, and let $\hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$. Suppose for now that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to a normal distribution $\distv(P)$ in a model space $\mathcal{M}_0$.  Any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$. Letting $\rvv$ be distributed $\distv(\disto)$, the region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
\begin{align}
  Pr_{\distv}\{\rvv \not \in \Theta_0(P)\} = 1 - \alpha \text{ for every } P \in \mathscr{M}_0.\label{eqn:alpha_rej}
\end{align}
While there are infinitely many regions satisfying \eqref{eqn:alpha_rej},  we focus on a particular class of regions defined using $\ell_p$ norms. For simplicity, first consider regions defined using an $\ell_2$ norm:
\begin{align*}
	\Theta_0(r) = \left\{\omega : \|\omega\|_2 \leq r\right\}.
\end{align*}
A region satisfying \eqref{eqn:alpha_rej} has a radius defined by: 
% \textcolor{blue}{be consistent on indexing ``$Pr$'' -- if you're going to write as $Pr_{Q(P)}$, do this throughout!}
\begin{align*}
	r_\alpha(\disto) = \min\left\{r : Pr_{\distv}(\|\rvv\|_2 \leq r) \geq 1 - \alpha \right\}.
\end{align*}
By constraining the possible regions we consider, we can now define our test by:
\begin{align*}
	\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha.
\end{align*}
Similarly, p-values can now be defined as $Pr_Q(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2)$.
%The quantity could also be used for a test, and since we know $Pr_Q(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\Psi}}(\rvo)\|_2)$ will be uniformly distributed on $(0, 1)$ asymptotically under the null, we can reject $H_0$ whenever this value is less than $\alpha$.
% As an example, a test is defined by a norm $p$ and level $\alpha$ which define the cutoff value;
% \begin{align*}
% 	c_{p, \alpha} = \min\left\{c : \frac{1}{B}\sum_{b = 1}^B I\left\{\|\boldsymbol{Z}_b\|_p \leq c\right\} \leq \alpha\right\},
% \end{align*}
% where $Z_1, \dots, Z_B$ are draws from $Q$. Reject the null if $\|\sqrt{n}\hat{\boldsymbol{\psi}}\|_p > c_{p, \alpha}$.

@@

% \subsection{\textcolor{blue}{Creating a rejection region using a function}}
Above, a norm mapped the distribution of $\rvv$ and value  of $\sqrt{n}\hat{\boldsymbol{\psi}}$ into $\mathbb{R}$.  This distribution and value in $\mathbb{R}$ can be used to  calculate a p-value. 
% \textcolor{blue}{I don't understand the end of this sentence}. 
This method for finding $p$-values can be used with more complicated functions. We can think of the above test as a function of the test statistic, $\sqrt{n}\hat{\boldsymbol{\psi}}$ and $\sqrt{n}\hat{\boldsymbol{\psi}}$'s limiting distribution.  For the purposes of a test, the distribution used to define any function will be the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ which is distributed according to a multivariate normal with a mean of zero. Because the variance covariance matrix of this multivariate normal (denoted $\Sigma$) \textcolor{blue}{is one-to-one with the possible distributions}, we will index our functions $\Gamma$ by $\Sigma$. 
% For every distribution $\distv$ with support contained in $\mathbb{R}^d$, let $\Gamma_{\distv}$ be a function mapping from  $\mathbb{R}^d$ to $\mathbb{R}$. The distribution of $\Gamma_\distv(\rvv)$ (where $\rvv \sim \distv$) can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test.  
% \textcolor{blue}{I see $\Gamma_{\distv}$ being an $\mathbb{R}^d$ to $\mathbb{R}$ function. I don't see $\Gamma_Q(x)$ being a function? I also don't understand how this maps ``from a ... distribution'' to anywhere? Do you mean: ``For any distribution $Q$ with support contained in $\mathbb{R}^d$, let $\Gamma_Q$ be a function mapping from $\mathbb{R}^d$ to $\mathbb{R}$''?}
An example of a more complicated function $\Gamma_\vmat$ is given below:
% any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.  Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.  However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.  
% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(\|\rvv\| \geq \|x\| \right)$.  For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.  However, for other $\Gamma$, this may not be the case. Consider

\begin{align}
	\Gamma_\vmat(x) &= Pr_\distv(\|\tilde\rvv + x\| > c_{0.8})  \text{ where }  c_{\vmat, 0.8} \equiv \min_{c}\{c : Pr_\distv(\|\tilde\rvv\| < c) \geq 0.8 \} \text{ and } \tilde\rvv \overset{d}{=} \rvv. \label{gamma:pow}
\end{align}
% \textcolor{blue}{What is $\tilde\rvv \overset{d}{=} \rvv$ telling us? Don't we already know that the probabilities over both of these quantities are indexed by $Q$? Also, why use different notation at all? Why not just $\rvv^*$ for both? Here because $c_{0.8}$ is not random so this is distinction does not need to be made.}
% In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\vmat(\sqrt{n}\hat{\boldsymbol{\psi}}, \|\cdot\|)$ to $\Gamma_\vmat(\rvv, \|\cdot\|).$

@@

While this method for defining tests allows for many different specifications, it often requires choosing a norm as part of the definition of $\Gamma$.  Figure \ref{fig:figure1} shows that the power a test achieves can depend on the norm chosen.  Consider the case when $d = 2$ and $100$ draws are taken from $Z$.  Cutoffs can be obtained by transforming these data (using the $\ell_p$ norm) and taking the 95\% quantile of this transformed data. The perimeter of the acceptance region when using the $\ell_2$ and $\ell_{\infty}$ norm are given in red and blue respectively. If $\sqrt{n}\hat{\boldsymbol{\psi}}$ falls within any of the purple regions, using the $\ell_\infty$ norm would result in failing to reject $H_0$ and using the $\ell_2$ norm would result in rejecting $H_0$.  The converse is true for the green regions.

\subsection{Adaptive selection of a norm}
In the previous section it was shown that a test can be defined by choosing a summarizing function and norm. However, the choice of norm influences the power of the test. In most scenarios it will not be clear a priori which norm will have maximal power for the true alternative. The procedure proposed in this section adaptively selects a norm and it will be shown that this procedure achieves greater power than a test with a fixed norm, while maintaining type 1 error control.

To achieve this, first define $\Gamma_{1, \vmat}(x), \dots, \Gamma_{p, \vmat}(x)$ as collection of functions in which the functions only differ by the norm used in their definition. Next, define
% by defining a $\Gamma$ to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.  For example, if we had $p$ different norms, $\norm_1, \dots, \norm_p$ and some summary function $\Gamma_\vmat(x, \|\cdot\|)$, we would define the adaptive version of $\Gamma$ as
\begin{align*}
	\Gamma^*_\vmat(x) = \max\left\{\Gamma_{1, \vmat}(x), \Gamma_{2, \vmat}(x), \dots, \Gamma_{p, \vmat}(x)\right\}.
\end{align*}
\textcolor{blue}{Change * so that they are not suppersetting both the rv and functions.}
\textcolor{blue}{This could be the min if smaller values indicate larger distances away from the norm (such as p-values).}

While this function is more complicated than before,  $\Gamma^*_{\vmat}(\rvv))$ can still be compared to $\Gamma^*_{\vmat}(\sqrt{n}\hat{\psi})$ to obtain a p-value. Also, while it may be difficult to obtain the exact distribution of $\Gamma_\vmat^*(\rvv)$, the distribution is a function of $\distv$, so obtaining very good approximations of $\Gamma_\vmat^*(\rvv)$ is possible by taking many draws from $\rvv$. This technique can be used both to estimate the function $\Gamma$ and to estimate $\Gamma^*_\vmat(\rvv)$ .

@@

\section{Discussion}

@@

% Above we used a norm to constrain the considered rejection regions and allow for a test based on the value of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under the norm the distribution of $\rvv$ under the norm, both of which reside in $\mathbb{R}$.

>>>>

\section{proposed testing procedure}
\label{sec:prop_test_proc}
% We want to define a test
% All tests in high dimensions can be defined using acceptance / rejection regions.
% First we consider a simple example. 
As with all tests, our test will be defined by an acceptance region 
Any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$. This region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
\begin{align}
  PR_{\distv}\{\rvv \not \in \Theta_0(p)\} = 1 - \alpha \text{ for every } P \in \mathscr{M}_0 \text{ where } \rvv \sim \distv(\disto).\label{eqn:alpha_rej}
\end{align}
While there are infinitely many regions satisfying \eqref{eqn:alpha_rej},  we focus for now on a particular class of regions defined using $\ell_p$ norms which will naturally lead to a straightforward testing procedure. For simplicity, first consider regions defined using an $\ell_2$ norm:
\begin{align}
	\Theta_0(r) = \left\{\omega : \|\omega\|_2 \leq r\right\}. \label{eqn:region}
\end{align}
a region satisfying \eqref{eqn:alpha_rej} and \eqref{eqn:region} has a radius defined by: 
% \textcolor{blue}{be consistent on indexing ``$pr$'' -- if you're going to write as $pr_{q(p)}$, do this throughout!}
\begin{align*}
	r_\alpha(\disto) = \min\left\{r : PR_{\distv}(\|\rvv\|_2 \leq r) \geq 1 - \alpha \right\}.
\end{align*}
By constraining the possible regions we consider, we can now define our test.  Let $\hat{\boldsymbol{\Psi}} : \mathbb{R}^d \to \mathbb{R}$ be an estimator of $\boldsymbol{\psi}$, and let $\Hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$. Suppose for now that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to a normal distribution $\distv(p)$ when $p$ is contained in the model space  $\mathcal{M}_0$.  Our test can be defined by 
\begin{align}
\label{eqn:simp_test}
	\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha,
\end{align} and 
 p-values can now be defined by $\text{Pr}_\distv(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2)$. This example illustrates how functions mapping into $\mathbb{R}$ (the $\ell_2$ norm in this case) allow us to define a test and p-value for $H_0$. Next consider this procedure in more generality.

% \subsection{\textcolor{blue}{Creating a rejection region using a function}}
Consider a function $\Gamma$, of a vector in $\mathbb{R}^d$ (corresponding to $\sqrt{n}\hat{\boldsymbol{\psi}}$) and a $d$ dimensional distribution function (corresponding to $\sqrt{n}\hat{\boldsymbol{\psi}}$'s limiting distribution). %For the example of the $\ell_2$ norm, the p-value calculation was a function of the limiting distribution $Z$ and the test statistic $\sqrt{n}\hat{\boldsymbol{\psi}}$
Because the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under $H_0$ is always a mean zero multivariate normal, we will index our general functions $\Gamma$ by the $d$ by $d$ variance covariance matrix instead of the infinite dimensional distribution function.
%   Under $H_0$, the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ will be a mean zero multivariate normal distribution. 
An example of a more complicated function $\Gamma_\vmat$ is given below:
% any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.  Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.  However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.  
% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(\|\rvv\| \geq \|x\| \right)$.  For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.  However, for other $\Gamma$, this may not be the case. Consider 
\begin{align}
	\Gamma_\vmat(x) &= Pr_\distv(\|\tilde\rvv + x\| > c_{0.8})  \text{ where }  c_{\vmat, 0.8} \equiv \min_{c}\{c : Pr_\distv(\|\tilde\rvv\| < c) \geq 0.8 \} \text{ and } \tilde\rvv \sim N(0, \Sigma). \label{gamma:pow}
\end{align}

% \textcolor{blue}{I don't understand the end of this sentence}. 
% While the the above test has nice properties (type one error control, consistency), it is not clear how this test will perform compared to other tests with similar properties.

@@

While we have outlined a way of defining different tests of $H_0$, the natural next question is which test will perform the best.  To explore this question, consider a simple example comparing the test described in equation \eqref{eqn:simp_test} with a test that is identical except it uses the maximum absolute value instead of $\ell_2$ norm.  Figure \ref{fig:figure1}, panel (A) illustrates these two tests in $\mathbb{R}^2$. One hundred draws are taken from a bivariate normal distribution with mean zero and identity covariance matrix. All observations in panel (A) except the five with the largest $\ell_2$ norm are contained within the red circle. The blue squares in each panel contains all observations except the five with the largest $\ell_\infty$ norm. 
\textcolor{blue}{The circle and square represent the cutoffs of tests using empirical estimates of the $95^{\text{th}}$ percentile of $\ell_2(Z)$ and $\ell_\infty(Z)$ respectively.}
Observations that fall within the purple region would result in a rejected null hypothesis if the $\ell_2$ norm was used to define the test, but not if the $\ell_\infty$ norm was used. The converse is true of the green region. Panels B shows draws from an alternative in which $\psi_2 \ne 0$ and $\psi_1 = 0$ and the $\ell_\infty$ norm performs better (achieves higher power). Panel C shows draws from an alternative in which $\psi_1$ and $\psi_2 \neq 0$ and the $\ell_2$ norm performs better.

While both acceptance regions are created so to achieve type $1$ error control, depending on the alternative one test will outperform the other. Panel $B$ shows an alternative in which only $\psi_2$ is non-zero.  Because the max norm only considers the largest coordinate, shifting each observations in only a single direction will have larger impact on the max norm of the observations compared to the $\ell_2$ norm.  This trend is shown by the numerous green observations outside of the blue box (equivalent to rejecting $H_0$) and inside the red circle (equivalent to failing to reject $H_0$). In contrast, there is only a single observation that is outside the red circle, and inside the blue box. The converse trend is shown in panel $C$. Here, the $\ell_2$ norm performs better, because it takes into account both coordinates of the shift whereas the $\ell_\infty$ norm can only take into account one of these coordinate shift.

The efficiency that can be gained from using the correct norm can be quite larger, especially when dimension grows.  Work done by \citep{pinelis_schur2-concavity_2014} states that even for dimensions as small as $3$ the gains in asymptotic efficiency can become arbitrarily large between two potential norms.

% For every distribution $\distv$ with support contained in $\mathbb{R}^d$, let $\Gamma_{\distv}$ be a function mapping from  $\mathbb{R}^d$ to $\mathbb{R}$. The distribution of $\Gamma_\distv(\rvv)$ (where $\rvv \sim \distv$) can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test.  
% \textcolor{blue}{I see $\Gamma_{\distv}$ being an $\mathbb{R}^d$ to $\mathbb{R}$ function. I don't see $\Gamma_Q(x)$ being a function? I also don't understand how this maps ``from a ... distribution'' to anywhere? Do you mean: ``For any distribution $Q$ with support contained in $\mathbb{R}^d$, let $\Gamma_Q$ be a function mapping from $\mathbb{R}^d$ to $\mathbb{R}$''?}
% \textcolor{blue}{What is $\tilde\rvv \overset{d}{=} \rvv$ telling us? Don't we already know that the probabilities over both of these quantities are indexed by $Q$? Also, why use different notation at all? Why not just $\rvv^*$ for both? Here because $c_{0.8}$ is not random so this is distinction does not need to be made.}
% In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\vmat(\sqrt{n}\hat{\boldsymbol{\psi}}, \|\cdot\|)$ to $\Gamma_\vmat(\rvv, \|\cdot\|).$

@@

\subsection{Adaptive selection of a norm}
In the previous section we showed that a test can be defined with a summarizing function and norm. However, the choice of norm can influence the power of the test. In most scenarios it will not be clear a priori which test will have maximal power for the true alternative. The procedure proposed in this section adaptively selects a norm and it will be shown that this procedure achieves greater power than a test with a fixed norm, while maintaining type 1 error control.

To achieve this, first define $\Gamma_{1, \vmat}(x), \dots, \Gamma_{p, \vmat}(x)$ as collection of functions in which the functions only differ by the norm used in their definition. Next, define
% by defining a $\Gamma$ to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.  For example, if we had $p$ different norms, $\norm_1, \dots, \norm_p$ and some summary function $\Gamma_\vmat(x, \|\cdot\|)$, we would define the adaptive version of $\Gamma$ as
\begin{align*}
	\Gamma^*_\vmat(x) = \max\left\{\Gamma_{1, \vmat}(x), \Gamma_{2, \vmat}(x), \dots, \Gamma_{p, \vmat}(x)\right\}.
\end{align*}
\textcolor{blue}{This could be the min if smaller values indicate larger distances away from the norm (such as p-values).}

While this function is more complicated than before,  $\Gamma^*_{\vmat}(\rvv))$ can still be compared to $\Gamma^*_{\vmat}(\sqrt{n}\hat{\psi})$ to obtain a p-value. Also, while it may be difficult to obtain the exact distribution of $\Gamma_\vmat^*(\rvv)$, the distribution is a function of $\vmat$, so obtaining good approximations of $\Gamma_\vmat^*(\rvv)$ is possible by taking many draws from $\rvv$.

@@

\section{Discussion}
\begin{itemize}
	\item The most generalizable methods for hypothesis testing suffer from poor power, and ignore correlation between covariates.
	\item Tests with high power are often difficult to generalize, working only for a single parameter, or relying on parametric assumptions.
	\item We find a happy medium in this article.
	\item Our method has comparable power to tailor made methods, without require modeling assumptions or parameters of interest.
	\item We showed the methods flexibility through the use of three different data examples that include missing data and a causual model.
	\item This method can also be expanded by using different $\Gamma$ functions, potentially optimizing of entire classes of $\Gamma$ functions with machine learning algorithms.
	\item Also look at multiplying $\sqrt{n}\hat{\boldsymbol{\psi}}$ by inverse of influence function. 
	\item There are issues with using parametric bootstrap, which can be avoided in certain cases by using a permutation test.
\end{itemize}

\section{Conclusion}

@@

% Above we used a norm to constrain the considered rejection regions and allow for a test based on the value of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under the norm the distribution of $\rvv$ under the norm, both of which reside in $\mathbb{R}$.
%the quantity could also be used for a test, and since we know $pr_q(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}(\rvo)\|_2)$ will be uniformly distributed on $(0, 1)$ asymptotically under the null, we can reject $h_0$ whenever this value is less than $\alpha$.
% as an example, a test is defined by a norm $p$ and level $\alpha$ which define the cutoff value;
% \begin{align*}
% 	c_{p, \alpha} = \min\left\{c : \frac{1}{b}\sum_{b = 1}^b i\left\{\|\boldsymbol{z}_b\|_p \leq c\right\} \leq \alpha\right\},
% \end{align*}
% where $z_1, \dots, z_b$ are draws from $q$. reject the null if $\|\sqrt{n}\hat{\boldsymbol{\psi}}\|_p > c_{p, \alpha}$. 
%the quantity could also be used for a test, and since we know $pr_q(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}(\rvo)\|_2)$ will be uniformly distributed on $(0, 1)$ asymptotically under the null, we can reject $h_0$ whenever this value is less than $\alpha$.
% as an example, a test is defined by a norm $p$ and level $\alpha$ which define the cutoff value;
% \begin{align*}
% 	c_{p, \alpha} = \min\left\{c : \frac{1}{b}\sum_{b = 1}^b i\left\{\|\boldsymbol{z}_b\|_p \leq c\right\} \leq \alpha\right\},
% \end{align*}
% where $z_1, \dots, z_b$ are draws from $q$. reject the null if $\|\sqrt{n}\hat{\boldsymbol{\psi}}\|_p > c_{p, \alpha}$.
